Lynott et al. (2014) - Potential error in statistics reporting

### 2017-11-17 manuscript.Rmd
Minor edits in abstract

abstract: >
  Psychologists must be able to test both for the presence of an effect and for the the absence of an effect. In addition to testing against zero, researchers can use the Two-One-Sided Tests (TOST) procedure to test for *equivalence* and reject the presence of a smallest effect size of interest (SESOI). TOST can be used to determine if an observed effect is surprisingly small, given that a true effect at least as large as the SESOI exists. We explain a range of approaches to determine the SESOI in psychological science, and provide detailed examples of how equivalence tests should be performed and reported. Equivalence tests are an important extension of statistical tools psychologist currently use, and enable researchers to falsify predictions about the presence, and declare the absence, of meaningful effects.

>>>>

abstract: >
  Psychologists must be able to test both for the presence of an effect and for the absence of an effect. In addition to testing against zero, researchers can use the Two One-Sided Tests (TOST) procedure to test for *equivalence* and reject the presence of a smallest effect size of interest (SESOI). TOST can be used to determine if an observed effect is surprisingly small, given that a true effect at least as large as the SESOI exists. We explain a range of approaches to determine the SESOI in psychological science, and provide detailed examples of how equivalence tests should be performed and reported. Equivalence tests are an important extension of statistical tools psychologist currently use, and enable researchers to falsify predictions about the presence, and declare the absence, of meaningful effects.
